Capstone Movielens Report

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: regularize.test_lambda.UMGY_effect.cv.

#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) Function {#func.calc_UMGY_effect_RMSE.cv}
\

@@

@@

::: {.noteblock data-latex=""}
This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.

@@

The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
           CVFolds_N, 
           UMGY_effect_RMSE)

@@

::: {.noteblock data-latex=""}
The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) script on _GitHub_.
:::
:::

@@

#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMGY_effect.cv}
\

@@

```{r eval=FALSE}
lambdas <- seq(0, 0.2, 0.01)
cv.UMGYE.preset.result <- 
  tune.model_param(lambdas, regularize.test_lambda.UMGY_effect.cv)
```

@@

The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is shown below:
```{r eval=FALSE}
regularize.test_lambda.UMGY_effect.cv <- function(lambda){
  umgy_effect <- train_user_movie_genre_effect.cv(lambda)
  calc_user_movie_genre_effect_RMSE.cv(umgy_effect)
}
```

::: {.noteblock data-latex=""}
The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L147) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) script on _GitHub_.
:::
:::

>>>>

#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) Function {#func.calc_UMGY_effect_RMSE.cv}
\

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *This Appendix*.
:::

@@

::: {.noteblock data-latex=""}
This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.

@@

The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is shown below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
           CVFolds_N, 
           UMGY_effect_RMSE)

@@

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) script on _GitHub_.
:::
:::

@@

#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGY_effect.cv}
\

@@

```{r eval=FALSE}
  lambdas <- seq(0, 512, 32)
  cv.UMGYE.preset.result <- 
    tune.model_param(lambdas, 
                     regularize.test_lambda.UMGY_effect.cv,
                     steps.beyond_min = 16)
```

@@

The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is shown below:
```{r eval=FALSE}
regularize.test_lambda.UMGY_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UMGY_effect.cv
`lambda` is `NA`")
  }

  train_UMGY_effect.cv(lambda) |>
    calc_UMGY_effect_RMSE.cv()
}
```

::: {.noteblock data-latex=""}
The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
:::
:::
